\section{Purpose and Scope of this document}
This document provides a detailed Project Plan for PowerEnjoy project. Its main objective is to outline the development process, establishing the estimated costs, duration and necessary resources, through an estimation of efforts and complexity. This document is only intended as an help to the Project Manager to define real budget and resources. 
\bigbreak
In the first chapter, \textit{Project Size, Effort and Costs estimation}, we try to estimate the project size and complexity using the Function Points analysis (providing estimated LOC), then proceeding to an estimation of costs and efforts. 
\bigbreak
In the second chapter, \textit{Planned Schedule}, we will use the previously found data to outline a possible schedule for the project itself, in all its part. 
\bigbreak
In the third chapter, \textit{Resource Allocation}, we will assign roles and tasks to our team members, using the previous schedule as an indicator.
\bigbreak
In the last chapter, \textit{Risk Management}, we will point out and analyze the possible risks in the development process, providing an analysis of damages they could generate and how they can be avoided. 

\section{Definitions, Acronyms and Abbreviations}
\begin{itemize}
\item \textbf{FP:} Function Points
\item \textbf{ILF:} Internal Logic File
\item \textbf{ELF:} External Logic File
\item \textbf{EI:} External Input
\item \textbf{EQ:} External Inquiry
\item \textbf{EO:} External Output
\item \textbf{LOC:} Lines Of Code
\item \textbf{SLOC:} Source Lines Of Code
\item \textbf{IFPUG:} International Function Point Users Group \href{http://www.ifpug.org}{IFPUG}
\end{itemize}

\section{Referenced Documents}
\begin{itemize}
\item Project Plan Sample from myTaxiService
\item Website \href{http://alvinalexander.com/FunctionPoints/FunctionPoints.shtml}{Alvin Alexander Website} for tables and definitions
\item Website \href{http://www.qsm.com/resources/function-point-languages-table}{Function Point Languages Table} for Javascript FP to SLOC conversion values.
\item \href{http://csse.usc.edu/tools/COCOMOII.php}{COCOMO online tool}
\item \href{http://csse.usc.edu/csse/research/COCOMOII/cocomo2000.0/CII_modelman2000.0.pdf}{COCOMO Model Specifications}
\end{itemize}