Here some possible scenarios of usage of this service:\\
\bigbreak
\bigbreak
\textbf{\large Scenario 1}
\bigbreak
It's about 9 in the morning and Ned, a well-known consultant, is leaving home to go to an important meeting. When he gets in his car and tries to start the engine the car refuses to turn on. Ned is very concerned because the meeting starts at 10 o'clock. Then he remembers of an advertising seen the day before, so he takes out his phone and looks for PowerEnJoy, a new, reliable car sharing service, on the App Store. He is in a hurry but he discovers that the registration mechanism is fast and intuitive. Since the system can recognise and extract information from pictures, he only needs to take a photo of his credit card and driving licence and that's it, few seconds later he is ready to make a reservation using the map of near-by available cars on the application. He is really lucky, the nearest car is only 100m away from his position. When he reaches it he can unlock it directly with his phone. Thanks to this new service Ned managed to arrive on time to the meeting.\\
\bigbreak
\bigbreak
\textbf{\large Scenario 2}
\bigbreak
Anna is a lawyer and every week she must attend some court hearings at the central court of her city. Unfortunately, the central zone of the town has been declared off-limits to traffic to reduce air pollution. Since she is always carrying with her some important documents she cannot use public transport services. Recently she discovered that PowerEnJoy cars, being electric, can enter the city center. Now she uses PowerEnJoy portal every week to find and reserve cars near her house whenever she needs to go to the court for a hearing. 