Here we list some possible scenarios of usage of this service:\\
\bigbreak
\bigbreak
\textbf{\large Scenario 1}
\bigbreak
It's about 9 in the morning and Ned, a well-known consultant, is leaving home to go to an important meeting. When he gets in his car and tries to start the engine the car refuses to turn on. Ned is very concerned because the meeting starts at 10 o'clock. Then he remembers of an advertising seen the day before, so he takes out his phone and looks for PowerEnJoy, a new, reliable car sharing service, on the App Store. He is in a hurry but he discovers that the registration mechanism is fast and intuitive. Since the system can recognise and extract information from pictures, he only needs to take a photo of his credit card and driving licence and that's it, few seconds later he is ready to make a reservation using the map of near-by available cars on the application. He is really lucky, the nearest car is only 100m away from his position. When he reaches it he can unlock it directly with his phone. Thanks to this new service Ned managed to arrive on time to the meeting.\\
\bigbreak
\bigbreak
\textbf{\large Scenario 2}
\bigbreak
Anna is a lawyer and every week she must attend some court hearings at the central court of her city. Unfortunately, the central zone of the town has been declared off-limits to traffic to reduce air pollution. Since she is always carrying with her some important documents she cannot use public transport services. Recently she discovered that PowerEnJoy cars, being electric, can enter the city center. Now she uses PowerEnJoy portal every week to find and reserve cars near her house whenever she needs to go to the court for a hearing. Moreover, when she needs to go back home she uses PowerEnjoy application on her Android smartphone. \\
\bigbreak
\bigbreak
\textbf{\large Scenario 3}
\bigbreak
Riccardo is an exchange student who wants to go and see the basketball match at the Arena tonight. Since he has no car he wants to use PowerEnJoy car sharing service to get there. In order to reduce the cost of the ride he decides to pick up some friends on his way. When the new passengers get into the car the seats automatically detect them and the system applies a 10\% discount. When he arrives near the Arena the screen on the car notifies Riccardo the presence of a recharging station close to his position. Hence he decides to park at the station and plug the car to the power station. Then, with his phone, he terminates the rental and the application informs him that he obtained a 40\% total discount. He is really happy with the service and decides to use it also to go back home.\\
\bigbreak
\bigbreak
\textbf{\large Scenario 4}
\bigbreak
Roman is the system administrator of PowerEni. Today, as usual, he is working at PowerEni Headquarter. During his workday he receives a request from the human resources department saying that a new worker, Karim, has been hired. Roman is required to register the new employee in the system. To do that he opens an ad hoc tool on his computer. The tool provides an intuitive user interface for the management of workers' accounts. After having processed the information of the new worker the system prints his new badge and writes a unique NFC signature on it. Few minutes later Karim arrives at the Headquarter and picks up his badge. Then he downloads PowerEniWorker application, creates an account, activates it using the NFC tag and finally registers his fingerprint for future usage. Karim is ready to start working for PowerEni\\
\bigbreak
\bigbreak
\textbf{\large Scenario 5}
\bigbreak
Karim is a worker at PowerEni. At the beginning of his workday he opens his PowerEniWorker application and logs in using either his fingerprint or the NFC signature of his identification badge. Automatically the system marks his status as ``available" and starts computing a suitable personalised task for the worker. Meanwhile, not far away from Karim's position, Alan, a user, is reporting a flat tire on his car using the dedicated button on PowerEnJoy application. The system terminates Alan's rental and marks the car as ``to be repaired". Since Karim is the nearest available worker, the server sends him a push notification with all the information needed to reach and repair Alan's car. Therefore Karim accepts the task, changing his status to ``busy", and gets in his electric van (provided by PowerEni). Once he reaches the faulty car he fixes the flat tire. Finally, always using PowerEniWorker application, he marks the task as ``done". The system reacts assigning a new task to Karim and changing the status of the car to ``available". \\
