\section{Purpose}
The purpose of this document is to give a more detailed and technical overview about PowerEnJoy system. \\
This document is addressed to developers and aims to identify:
\begin{itemize}
\item The high level architecture;
\item The design patterns;
\item The main components and their interfaces provided one for another;
\item The Runtime behaviour.
\end{itemize}

\section{Scope}
This document will present different level views in order to describe clearly the architecture of PowerEnJoy System. In particular we will present the component view, both high and low level, the runtime view and a further description of user interface, analysed in its runtime flow.\\
The System is based on two mobile applications and a web application. \\
As already explained in the RASD, the targets for the Service are: 
\begin{itemize}
\item The Drivers;
\item The Workers;
\item The Admins.
\end{itemize}
The System allows the Drivers to reserve cars from both the mobile application and the web portal. At the same time it manages the the status of the cars and, if necessary, assigns tasks to the Workers via an ad-hoc mobile application. The Admins of the System can interact with the web portal to make privileged actions.

\section{Definitions, Acronyms and Abbreviations}
\begin{description}
\item [Driver] Client of the system, i.e. the one that uses the service, reserves and drives. Every Driver must provide personal informations (name, surname, email, birthdate, a valid license and payment information;
\item [Ride] A single usage of the service, starts when the user turn on the engine, stops when the car is locked inside a Safe Area;
\item [Blocked driver] A driver that has an invalid license or invalid payment coordinates;
\item [Worker] Employee of the company, perform physical actions (moving, charging etc) on cars;
\item [Report] Car issue reported by the Driver during a Drive. Will later be assigned to a Worker;
\item [Task] Piece of work assigned to a worker. Different type of tasks are described later. Every task assigns a single car to a single worker;
\item [Administrator] Employee of PowerEni that is in charge of the administration of the system through the administration console;
\item [Drop off] The act of leaving the car inside a safe area. This ends the service provided to the driver and effectively make the driver pay;
\item [Safe Area] An area in which the Driver can park the car and stop the Service;
\item [RASD] Requirements Analysis and Specifications Document;
\item [DD] Design Document;
\item [API] Application Programming Interface; 
\item [DBMS] DataBase Management System;
\item [UI] User Interface;
\item [REST] REpresantional State Transfer.
\end{description}

\section{Reference Documents}
\begin{itemize}
\item The RASD we released before;
\item Sample Design Deliverable Discussed on Nov. 2.pdf.
\end{itemize}

\section{Document Structure}
\begin{description}
\item [Introduction:] contains an overall description of the content and the structure of the document;
\item [Architecture:] this section contains:
\begin{itemize}
\item \textbf{Overview:} coarse view of the System i.e. the division in tiers;
\item \textbf{High Level Components:} description of the main components of the application and their interaction;
\item \textbf{Tracking Vehicle State:} more detailed description of the vehicle tracking mechanism;
\item \textbf{Core Component:} describes the inner composition of the core component;
\item \textbf{Relevant State Charts:} gives a deeper explanation of the dynamic behaviour of the model using State Charts;
\item \textbf{Runtime View:} contains some Sequence Diagrams of the main actions of the System;
\item \textbf{Interfaces:} contains the interfaces of all the subcomponents of the Core Component.
\end{itemize}
\item [Algorithm Design:] we will present some algorithms with pseudocode to show the logic of the most important parts of the System;
\item [User Interface Design:] starting from the ideas we gathered in the RASD we will give a deeper description of the UI;
\item [Requirements Traceability:] An explanation of how our architectural choices respect the requirements described in the RASD.
\end{description}







